---
title: Tyranny of the Fees
author: Jonathan Rossouw
date: 20858345
output:
  md_document:
    variant: markdown_github
---

# Purpose

This project consists of recreating the figures found at https://www.fmx.nfkatzke.com/posts/2020-08-05-practical-1/ which display the cumulative return of the FTSE JSE Allshare Index since January 2002 and January 2010 under different management fees structures.


```{r, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
pacman::p_load(fmxdat, tidyverse, lubridate, extrafont, glue, xtable)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

# Fee Impact on Cumulative returns since 2002

```{r fig_2002, include=TRUE, eval=TRUE, fig.cap="Fee Impact on Cumulative Returns since January 2002"}
# Load Data
dat <- list(fmxdat::Jalshtr)
# Set Different Fees
bp_name <- as.list(c(0, 10, 50, 100, 200, 250, 350))
# Create cumulative return series for different fees
gg <- map2_df(.x = dat, 
              .y = bp_name,
              ~cum_ret_func(dat = .x, bp = .y))
# Create tibble of relative performance
sum_gg <- comp_cum_ret(gg)
# Plot cumulative performance for full data set
gg_plot <- cum_ret_plot(gg, sum_gg)
gg_plot
```

```{r}
kableExtra::kable(sum_gg %>% select(bp, prop), caption = "Relative Impact of Fees on Wealth since 2002")
```

The above figure illustrates the impact that different fees structures have on cumulative returns since 2002. The figure shows the impact of a fee of 10, 50, 100, 200, 250, and 350 bps per annum on the cumulative returns of the FTSE JSE All Share Index since January 2002. The table shows the cumulative effect on the proportion lost due to fess over the time period.

# Fee Impact of Cumulative returns since 2010

```{r fig_2010, include = TRUE, eval=TRUE, fig.cap="Fee Impact on Cumulative Return since January 2010"}
# Create cumulative return series for different fees
gg_10  <- map2_df(.x = dat[[1]] %>% filter(date >= as.Date("2010-01-01")) %>%  list(), 
                  .y = bp_name,
                  ~cum_ret_func(dat = .x, bp = .y))
# Create tibble of relative performance
sum_gg_10 <- comp_cum_ret(gg_10)
# Plot cumulative performance for reduced data set
gg_10_plot <- cum_ret_plot(gg_10, sum_gg_10)
gg_10_plot
```

```{r}
kableExtra::kable(sum_gg_10 %>% select(bp, prop), caption = "Relative Impact of Fees on Wealth since 2010")
```

The above figure similarly illustrates the impact that different fees structures have on cumulative returns but since 2010. The figure shows the impact of a fee of 10, 50, 100, 200, 250, and 350 bps per annum on the cumulative returns of the FTSE JSE All Share Index since January 2010. The table shows the cumulative effect on the proportion lost due to fess over the time period.
